The non-random assembly of network motifs in  \nplant-pollinator networks

### 2023-01-10 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Minor changes on introduction and discussion

Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013]. Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @guimaraes2017]. Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014]. In part because conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019]. However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019]. These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002]. Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020]. However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).

>>>>

Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013]. Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @vieira2015; @guimaraes2017]. Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [but see\, @bergamo2021; @moeller2004; @sargent2008; @carvalheiro2014]. In part because conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019]. However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019]. These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002]. Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020]. However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
